%
% do not add anything in this part
%
\ifx\onefile\undefined

	\documentclass{article}

	%if tcolorbox and tikz are installed use next line
	\usepackage[tcbox]{projectalgo}
	\usepackage{projectalgo}
	\usepackage{algorithm2e}
	% replace type by one of graph, math, combinatory, string, network, datastructure, ai, image
	\pbtype{string}

	\begin{document}
\fi

%
% things can be added below
%

\def\pbname{Finite state machine minimization} %change this, do not use any number, just the name

\section{\pbname} 

% only for overview, so short description (no more than 1-2 lines)
\begin{overview}
\item [Algorithm:] Finite state machine minimization~(algo.~\ref{problem74}) 
	% - replace nb with problem number (e.g. problem101)
	% -	must match the label of the algorithm 
	% - for more than one algo list each of them and use problem101a, problem101b, problem101c etc.
\item [Input:] A finite state machine
\item [Complexity:] Average complexity $O(n \log \log n)$
\item [Data structure compatibility:] Finite state machine (Deterministic finite automaton)
\item [Common applications:] compilers, network protocols, theory of computation
\end{overview}



\begin{problem}{\pbname}
	Given a finite state machine, minimize the states.
\end{problem}

\subsection*{Description}
%Detailed description of the problem; More detailed information on the input and complexity; more applications with details on how they relate to each other (if this is the case).
\begin{enumerate}
\item Definition of FSM

The formal definition of a finite state machine (deterministic finite automaton) is 
\[
	M:~(Q, \Sigma, \delta, q_0, F)
\]
\begin{enumerate}
\item $Q$: finite set of states
\item $\Sigma$: finite set of input symbols
\item $\delta: Q\times \Sigma \rightarrow Q$: transition function 
\item $q_0 \in Q$: initial state
\item $F \subseteq Q$: accept state
\end{enumerate}
The automaton will accept a string $w$ if it starts at start state $q_0 $, and given each character in $w$, the transition rule will transit state to state according to $\delta$, and the final state shall halt at $F$ states.

\item Input 

The input of the algorithm shall be a well-defined finite state machine. Any illegal input should not be considered.

\item Complexity

%The time complexity of this algorithm is defined by the cost of each iteration and iteration time. For the outer iteration, it will need at most $|\Sigma|$ iterations, and for the inner iteration, it will need around $|F|$ operations. Thus we will need $O(|\Sigma|\cdot |F|)$ complexity.

For the complexity calculation, it is given by 2 theorems. The first theorem is described as :
\begin{center}
For any fixed integer $k\geq 2$ and for the uniform distribution over the deterministic and complete automata with n states over a k-letter alphabet, the average complexity of Moore’s state minimization algorithm is $\mathcal{O}(n \log \log n)$.
\end{center}
The proof of this theorem is generally as: The average number of iteration is given by
\[
	N_n=\frac{1}{A_n} (\sum_{i=0}^{n-2} (i+1) *|A_n|)
\]
Then define $\lambda_n= \lceil \log_k \log_2 n^3 +2 $, then an upper bound can be obtained as 
\[
	N_n \leq \frac{\lambda_n+1}{|A_n|} \sum_{i\leq \lambda_n} |A_n^i|+
	\frac{5\log_2n+1}{|A_n|} \sum_{i = \lambda_n+1}^{5 \log_2 n} |A_n^i|+
	\frac{n-1}{|A_n|} \sum_{i = 5 \log_2 n+1}^{n-2} |A_n^i|
\]	
And we find the third term to have time complexity $\mathcal{O}(1)$. And the rest term has time complexity $\mathcal{O}(n\log\log n )$

\item Application

In computer science field, finite state machine can be used to treat string. It can set up several states to check whether to accept an arrival of strings or not.


In digital circuits field, finite state machine can be used to depict the behavior of a certain circuit, and it could link the combinatoric circuits with a desired function.


Finite State Machine can also be used to depict a lot of behaviors in natural science or social science. For example, it could be applied to analyze the relation in different social characters, and to analyze how an social event is carried out.


\item Detailed Algorithm

This algorithm is introduced by \textit{Hopcroft}. The idea behind is called \textbf{partition refinement}, which means partition a large set into several small sets by their behavior, and after each iteration, the partition will be improved, till we reach the final result when the partition can no longer be refined. The detailed way of the algorithm works as follows.
\begin{enumerate}
\item 
At the very beginning, the are partitioned into two different groups, that is $\{F\}$ and $\{Q\backslash F\}$. These two groups are accepting states and rejecting states, obviously they are inequivalent.

\item 
Then it comes with the magic of this algorithm. That it separates $\{A\}$ with $\{W\backslash A\}$, where $W$ initially to be $F$. Then it separates the states whose result will lead to different sets which have been separated before, namely, after the $\delta$ transition, the next states from the current states are not equivalent. 

\item 
And if we keep going with this method, when we reach an iteration after which the result no longer changes, we can tell that we reach the optimized FSM.
\end{enumerate}
\newpage
% add comment in the pseudocode: \cmt{comment}
% define a function name: \SetKwFunction{shortname}{Name of the function}
% use the defined function: \shortname{$variables$}
% use the keyword ``function'': \Fn{function name}, e.g. \Fn{\shortname{$var$}}
\begin{Algorithm}[FSM minimization\label{problem74}]
	% - replace nb with problem number (e.g. problem101)
	% -	must match the reference in the overview
	% - when writing more than one algo use problem101a, problem101b, problem101c etc.
	%\SetKwFunction{myfunction}{MyFunction}	
	\SetKwFunction{min}{MinimizeFSM}
	\Input{A formally defined FSM}
	\Output{Minimized FSM}
	\Fn{\min{$M:~(Q, \Sigma, \delta, q_0, F)$}}{
		set $P$ $\leftarrow$ $\{F, Q\backslash F\}$; \cmt{Described in Description.5.(a)}\\
		set $W$ $\leftarrow$ $\{F\}$\;
		\While{$W \neq \varnothing$ }{
			Choose $A \in W$\;
			$W \leftarrow W \backslash A$\;
			\For{$s$ in $\Sigma$}{
				X $\leftarrow$ $\{X: \delta(X \times c) \rightarrow A\}$; \cmt{In natural language, it means that X is a state that: the transition rule takes $c$ in the state $X$ will go to a state in set $A$} \\	
				\For{$Y \subset P$ s.t. $X \cap Y \neq \varnothing$ $\and$ $Y \backslash X \neq \varnothing$}{
				\cmt{These two steps partition one set into two other inequivalent sets according to the definition of $X$}\;
				remove $Y$ in $P$\; 
				add $X \cap Y$ and $Y \backslash X$ to $P$\; 
				\uIf{$Y$ in $W$}{
					remove $Y$ in $W$\;
					add $X \cap Y$ and $Y \backslash X$ to $W$\; 
				}
				\Else{
				\cmt{These two steps add the newly found smaller set of equivalent states to $W$}\\
					\uIf{$|X\cap Y| \leq |Y\backslash X|$}{
						add $(X \cap Y)$ to $W$\; 
					}
					\Else{
						add $(Y \backslash X)$ to $W$\;
					}
				}	
				}
			}
		}
	}
	%	\Fn{\myfunction{$a,b$}}{
	%	}
	\BlankLine

	\Ret P

\end{Algorithm}
\end{enumerate}
\subsection*{References}
% list references where to find information on the given problem
% prefer books, research articles, or internet sources that are likely to remain available over time
% as much as possible offer several options, including at least one which provide a detailed study of the problem
% if available include links to programs/code solving the problem

\begin{itemize}\itemsep .125cm
	\item Foundation of Data Science, 2017, ~\url{https://www.cs.cornell.edu/jeh/book.pdf}
	\item Lawson, Mark V. (2004). Finite automata. Chapman and Hall/CRC. ISBN 1-58488-255-7. 
	\item Sakarovitch, Jacques (2009). Elements of automata theory. Translated from the French by Reuben Thomas. Cambridge: Cambridge University Press. ISBN 978-0-521-84425-3. 
	
\end{itemize}

\ifx\onefile\undefined
	\end{document}
\fi
