%
% do not add anything in this part
%
\ifx\onefile\undefined

	\documentclass{article}

	%if tcolorbox and tikz are installed use next line
	\usepackage[tcbox]{projectalgo}
	\usepackage{projectalgo}
	\usepackage{algorithm2e}
	%\usepackage[linesnumbered,ruled,longend]{algorithm2e}
	% replace type by one of graph, math, combinatory, string, network, datastructure, ai, image
	\pbtype{type}

	\begin{document}
\fi

%
% things can be added below
%

\def\pbname{Clique Problem} %change this, do not use any number, just the name

\section{\pbname} 

% only for overview, so short description (no more than 1-2 lines)
\begin{overview}
\item [Algorithm:] Finding maximum clique in a given graph~(algo.~\ref{problem22}) 
	% - replace nb with problem number (e.g. problem101)
	% -	must match the label of the algorithm 
	% - for more than one algo list each of them and use problem101a, problem101b, problem101c etc.
\item [Input:] An undirected graph with a set of vertices $V$ and a set of edges $E$.
\item [Complexity:] $\mathcal{O}(2^{n^{1-\epsilon/r^{1+\epsilon}}})$
\item [Data structure compatibility:] Undirected Graphs.
\item [Common applications:] DNA computing, sociology studies, data mining.%most common fields where this algorithm is used
\end{overview}

\begin{problem}{\pbname}
	The clique problem is to find the maximum clique in a given undirected graph. A clique is defined as all nodes are connected to each other through an edge, namely a complete subgraph.
\end{problem} 

\subsection*{Description}
\begin{enumerate}
\item Problem Clarification

%Detailed description of the problem; More detailed information on the input and complexity; more applications with details on how they relate to each other (if this is the case).
 Suppose we have an undirected graph with a set of vertices and a set of edges, we wish to find a fully connected subgraph with maximum nodes, which is known as a \textit{maximum complete subgraph}. The input 
 shall be the undirected graph. 

 \item Algorithm Clarification

 We will introduce a basic algorithm used to solve the clique problem, the method used is called \textbf{B\&B framework}. (Branch and Bound) In algo.~\ref{problem22}, it uses two key sets, $C$ represents the clique and $P$ represents all candidate vertices. The formal definition of $P$ is :
 \[
  	P \subset V\backslash C \cap \{\forall v \in P, \forall u \in C, {u,v} \in E\}
 \] The key operation of this algorithm is on line 10 and 11, line 10 is the bounding criteria, and line 11 is the branching condition. 
 \begin{enumerate}
 \item Bound: Since we need to maximize $C*$, from the definition of the graph, $|C|+|P|$ necessarily defines a maximum bound for the clique, and if our currently discovered clique is larger than $|C|+|P|$, we shall stop since we have already found the largest clique.
 \item Branch: During the branch operation, the property of $P$ must be maintained. So each time we update $P$ as $P \ \cap $ adjacent vertices to $p$. And $p$ is chosen as the vertices from smallest degree to biggest degree.
 \end{enumerate}
After each iteration, it will lead to either a bigger clique, or the function will halt on the bound condition.

\item  Applications with Details and complexity

The clique problem can be applied into many specific fields, such as DNA computing, sociology studies, data mining.

We will discuss about an abstract application, that the clique problem can be related with a standard quadratic programming problem in graph. The problem is defined as
\begin{center}
To maximize $\displaystyle \sum_{i=1}^n w_ix_w $, given that 
$
	x_ix_j =0 ~~\forall{i,j}\in E, x_i^2-x_i = 0
$
\end{center}
Let $A_G = (a_{ij})_{i,j\in V} $ be the adjacency matrix of $G$, and $g(x)=x^{T}A_Gx$. The global optimal solution is $x*$ that \[
	\omega(G) = \frac{1}{1-g(x*)}
\]
The $\omega(G)$ is the maximum clique of $G$.
The computational complexity of this problem is given by $\mathcal{O}(2^{n^{1-\epsilon/r^{1+\epsilon}}})$.%$\mathcal{O}^*(\gamma^n),(\gamma<2)$, with $\mathcal{(O)}^*$ means $\mathcal{(0)}$ ignoring the polynomial factors.  
\end{enumerate}
% add comment in the pseudocode: \cmt{comment}
% define a function name: \SetKwFunction{shortname}{Name of the function}
% use the defined function: \shortname{$variables$}
% use the keyword ``function'': \Fn{function name}, e.g. \Fn{\shortname{$var$}}
\begin{Algorithm}[Maximum Clique Problem\label{problem22}]
	% - replace nb with problem number (e.g. problem101)
	% -	must match the reference in the overview
	% - when writing more than one algo use problem101a, problem101b, problem101c etc.
	%\SetKwFunction{myfunction}{MyFunction}	
	\Input{A graph $G$}
	\Output{Clique $C$}
	%	\Fn{\myfunction{$a,b$}}{
	%	}
	\SetKwFunction{main}{Main}
	\SetKwFunction{clique}{Clique}
	\Fn{\main{G}}{
		\cmt{C* is the current discovered maximum clique}\\
		C* $\leftarrow$ $\varnothing$\;
		\clique{C*,$\varnothing$, $V$}\;
		\Ret{C*}\;
	}
	\BlankLine
	\Fn{\clique{set C*, set C, set P}}{
		\cmt{$C$ is clique, $P$ is candidate vertex set}
		\cmt{$|C|$ means the cardinality of $C$}\\
		\If{$|C| > |C*|$}{ 
			C* $\leftarrow$ C\;
		}
		\If{$|C|+|P|>|C*|$}{
			\For{$p$ sorted with degree-ascending in $P$}{
				P $\leftarrow$ P $\backslash$ $\{p\}$ \;
				C' $\leftarrow$ C $\cup$ $\{p\}$\;
				P' $\leftarrow$ P $\cap$ vertices adjacent to $p$\;
				\clique{set C*, set C', set P'} \;
			}
		}
	}
\end{Algorithm}
\subsection*{References}
% list references where to find information on the given problem
% prefer books, research articles, or internet sources that are likely to remain available over time
% as much as possible offer several options, including at least one which provide a detailed study of the problem
% if available include links to programs/code solving the problem

\begin{itemize}\itemsep .125cm
%	\item If available provide URLs, e.g.~\url{http://mywebsite.org}
	%\item ~\url{http://www.cs.ecu.edu/karl/6420/spr16/Notes/NPcomplete/clique.html}
	\item Ausiello, G., Crescenzi, P., Gambosi, G., Kann, V., Marchetti-Spaccamela, A., \& Protasi, M. (1999). Complexity and approximation: Combinatorial optimization problems and their approximability properties. Berlin: Springer.
	\item Babel, L., \& Tinhofer, G. (1990). A branch and bound algorithm for the maximum clique problem. Methods and Models of Operations Research, 34(3), 207–217.
	\item Engebretsen, L., \& Holmerin, J. (2003). Towards optimal lower bounds for clique and chromatic number. Theoretical Computer Science, 299(1–3), 537–584.
\end{itemize}

\ifx\onefile\undefined
	\end{document}
\fi
